---
output: github_document
title: "Simple practice for creating a makefile using Palmer penguins data"
author: "David Gerard"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Introduction

This is a simple exercise for creating a makefile to manage a small project that examines the really cool [Palmer Penguins data](https://allisonhorst.github.io/palmerpenguins/).

The files in the final report are:

- Makefile
- Readme.Rmd
- Readme.md
- analysis
    - classify_penguins.R
    - penguin_report.qmd
    - plot_penguin.R
- output
    - penguin_class.csv
    - penguin_pairs.png
    - penguin_report.html

These files have the following dependency structure:

```{r dependency-graph, message = FALSE, echo = FALSE}
library(tidyverse)
library(ggdag)
set.seed(15)
dagify("penguin_pairs.png" ~ "plot_penguin.R",
       "penguin_class.csv" ~ "classify_penguins.R",
       "penguin_report.html" ~ "penguin_pairs.png",
       "penguin_report.html" ~ "penguin_class.csv",
       "penguin_report.html" ~ "penguin_report.qmd") %>%
  ggdag(layout = "sugiyama",
        text_col = "black",
        node = FALSE) +
  theme_void() +
  xlim(-0.5, 2.5)
```

# Instructions

0. Make sure you have the necessary R packages installed:

    ```{r, eval=FALSE}
    library(tidyverse)
    library(tidymodels)
    library(GGally)
    library(palmerpenguins)
    library(randomForest)
    library(gt)
    ```

1. Modify the Makefile to automatically manage this pipeline.

2. Run `make` in the terminal to generate all of the output (penguin_class.csv, penguin_pairs.png, and penguin_report.html)

3. Change the color scheme in the pairs plot and re-run `make`.

4. Correct the date field in the YAML header in "penguin_report.html" and re-run `make`

